Biomarker screening

### 2022-04-28 code/r/02_D_numeric_vs_hpo_for_CRC.Rmd

ggsave(filename = glue('{CACHE_DIR}/CRC_labs_raw_data_distribution_by_rel_date.png'), plot = p, width = 8, height = 6)
```

@@

ggsave(glue("{CACHE_DIR}/plot_CRC_before_matching.png"), width = 2, height = 1.5)
p
```
```{r}
require(MatchIt)

@@

run_matchit <- function(filepath, force_rerun) {
  if (force_rerun | !file.exists(filepath)){
    # place m.out in the global environment with "<<-" (instead of regular "<-")
    m.out <<- matchit(outcome ~ medical_record_number, data = df_demographics_with_outcomes, method = "nearest", distance = df_demographics_with_outcomes$propensity_score)
    # save the matchit object in cache
    save(m.out, file=filepath)
  }
  load(file=filepath)
}

@@

ggsave(glue("{CACHE_DIR}/plot_CRC_after_matching.png"), plot = p, width = 2, height = 1.5)

@@

ggsave(filename = glue('{CACHE_DIR}/plot_CRC_age_gender_race_after_matching.png'), plot = plot_match, width = 6, height = 5)
plot(plot_match)
```
We need to put back the identifiers of controls to the database in order to selectively retrieve their labs. 
```{r}
dbExecute(dsca, "create temp table if not exists matched_control_cohort (medical_record_number VARCHAR)")

@@

crc_case_matched_controls_analysis %>% write.csv(file = glue('{CACHE_DIR}/crc_case_matched_controls_analysis.csv'), row.names = FALSE)

>>>>

ggsave2(filenames = c(glue('{OUT_DIR}/CRC_labs_raw_data_distribution_by_rel_date.png'), glue('{OUT_DIR}/CRC_labs_raw_data_distribution_by_rel_date.pdf')), plot = p, width = 8, height = 6)
```

@@

ggsave2(filenames = c(glue("{OUT_DIR}/plot_CRC_before_matching.png"), glue("{OUT_DIR}/plot_CRC_before_matching.pdf")), width = 2, height = 1.5)
p
```
```{r}
require(MatchIt)

@@

run_matchit <- function(filepath, force_rerun) {
  if (force_rerun | !file.exists(filepath)){
    # place m.out in the global environment with "<<-" (instead of regular "<-")
    m.out <<- matchit(outcome ~ medical_record_number, data = df_demographics_with_outcomes, method = "nearest", distance = df_demographics_with_outcomes$propensity_score)
    # save the matchit object in cache to the global environment
    save(m.out, file=filepath)
  }
  load(file=filepath, envir = globalenv())
}

@@

ggsave2(filenames = c(glue("{OUT_DIR}/plot_CRC_after_matching.png"), glue("{OUT_DIR}/plot_CRC_after_matching.pdf")) , plot = p, width = 2, height = 1.5)

@@

ggsave2(filenames = c(glue('{OUT_DIR}/plot_CRC_age_gender_race_after_matching.png'), glue('{OUT_DIR}/plot_CRC_age_gender_race_after_matching.pdf')), plot = plot_match, width = 6, height = 5)
plot(plot_match)
```
<br>
We need to put back the identifiers of controls to the database in order to selectively retrieve their labs. 
```{r}
dbExecute(dsca, "create temp table if not exists matched_control_cohort (medical_record_number VARCHAR)")

@@

crc_case_matched_controls_analysis %>% write.csv(file = glue('{OUT_DIR}/crc_case_matched_controls_analysis.csv'), row.names = FALSE)

### 2022-04-28 code/r/03_B_biomarker.Rmd

# cache directory to read from or write to
CACHE_DIR = '../../cache'

if (!dir.exists(CACHE_DIR)){
  dir.create(CACHE_DIR)
}

@@

write.csv(screen_results_annotated, file = glue('{CACHE_DIR}/screen_results_annotated.csv'), row.names = FALSE)

@@

write.csv(screen_results_annotated_formatted, file = glue('{CACHE_DIR}/screen_results_annotated.csv'), row.names = FALSE)

@@

sjPlot::tab_df(eosinophilia %>% rename(`Lab Year Bracket` = lab_date_rel_bracket), 
                title = 'Table Association of Eosinophilia with Severe Asthma',
               file = glue('{CACHE_DIR}/table_eosinophilia_with_severe_asthma.html'),
               alternate.rows = TRUE)

@@

```{r}
sjPlot::tab_df(significant_by_tested_and_observed_deduped %>% select(-distance_to_root, -lab_date_rel_bracket), 
                title = 'Table Selected Phenotypes (within 1 year prior) Associated with Severe Asthma',
               file = glue('{CACHE_DIR}/table_selected_biomarker_from_labs_within_1_year_prior_to_dx.html'), 
               alternate.rows = TRUE)
sjPlot::tab_df(significant_by_tested_and_observed_deduped_three_years %>% 
                 select(-distance_to_root) %>% rename(`Lab Year Bracket` = lab_date_rel_bracket), 
                title = 'Table Selected Phenotypes (within past 3 years) Associated with Severe Asthma',
               file = glue('{CACHE_DIR}/table_selected_biomarker_from_labs_within_3_years_prior_to_dx.html'),
               alternate.rows = TRUE)
```

>>>>

# cache directory to read from or write to
CACHE_DIR = '../../cache'
if (!dir.exists(CACHE_DIR)){
  dir.create(CACHE_DIR)
}

# output directory to write analysis results
OUT_DIR = '../../out'
if (!dir.exists(OUT_DIR)){
  dir.create(OUT_DIR)
}

@@

write.csv(screen_results_annotated, file = glue('{OUT_DIR}/screen_results_annotated.csv'), row.names = FALSE)

@@

write.csv(screen_results_annotated_formatted, file = glue('{OUT_DIR}/screen_results_annotated.csv'), row.names = FALSE)

@@

sjPlot::tab_df(eosinophilia %>% rename(`Lab Year Bracket` = lab_date_rel_bracket), 
                title = 'Table Association of Eosinophilia with Severe Asthma',
               file = glue('{OUT_DIR}/table_eosinophilia_with_severe_asthma.html'),
               alternate.rows = TRUE)

@@

```{r}
sjPlot::tab_df(significant_by_tested_and_observed_deduped %>% select(-distance_to_root, -lab_date_rel_bracket), 
                title = 'Table Selected Phenotypes (within 1 year prior) Associated with Severe Asthma',
               file = glue('{OUT_DIR}/table_selected_biomarker_from_labs_within_1_year_prior_to_dx.html'), 
               alternate.rows = TRUE)
sjPlot::tab_df(significant_by_tested_and_observed_deduped_three_years %>% 
                 select(-distance_to_root) %>% rename(`Lab Year Bracket` = lab_date_rel_bracket), 
                title = 'Table Selected Phenotypes (within past 3 years) Associated with Severe Asthma',
               file = glue('{OUT_DIR}/table_selected_biomarker_from_labs_within_3_years_prior_to_dx.html'),
               alternate.rows = TRUE)
```
